Estimation below the detection limit

### 2018-04-08 TEX/draft2.tex
Adding open question section to the ms

%
%In this section, we provide the details of the 2D experiment shown in Figure~\ref{fig:example}. In the experiment, we generated a sequence of $767\times 10^3$ 2D images (``micrograph") of size $2000\times 2000$. Each micrograph had around $\sim 900$ signal occurrences (depends on the stopping criterion that we need to explain) and in total $M = 561\times 10^6$. The noise level was $\sigma=1$.  
%
%To accelerate the experiment, we estimated only the first two autocorrelations of the signal. As mentioned in Section~\ref{sec:estimating_ac}, this data determines a 2D signal uniquely, up to possible reflection symmetry. 
%In this experiment, we chose the correct reflection manually. To estimate the signal we used the Relax-Reflect-Reflect (RRR) algorithm, which is a known phase retrieval algorithm. Recall that the second-order autocorrelation is equivalent to the power spectrum of the signal.
%Starting form random initialization of size $(2L-1)\times(2L-1)$, its $k$th  iteration take the form of 
% \begin{equation*}
% x_k = x_{k-1} + \beta(P_2(2P_1(x_{k-1}) -x_{k-1}) - P_1(x_{k-1}), 
%  \end{equation*}
% where $P_1$ is a projection that keeps the values of the  $L\times L$ entries in the upper-left corner and zeros out all other entries, $P_2$ is a projection that keeps the Fourier phase of $x_{k-1}$ and impose the correct Fourier magnitudes, and we set $\beta = 0.5$. The solution of the RRR scheme was used to initialized a LS estimation on the first two moments with signals of length $(2L-1)\times(2L-1)$ for the 200 iterations. Finally, we chose the $L\times L$ upper left corner and refined it using LS with 500 iterations. 
% 
\section{Conclusion} 
Here we conclude the paper. Points to mention;
\begin{itemize}
\item cryo -- EM
\item  structured background (here we assume i.i.d.\ noise -- can we remove it in some cases?)
\item   without separation   	
\item  sample complexity
\end{itemize}

%In particular, in cryo--EM, multiple projections of a molecule (signal), taken
%from unknown viewing directions, are recorded on two-dimensional detector
%array. Current algorithms try to detect these projections in a low SNR regime
%and then use them for the reconstruction process. Since the
%Then, the reconstruction problem is to detect these projection, and then use
%them to estimat
%The data acquired in both technologies is composed of multiple projections
%of a molecule (the signal), taken from unknown viewing direction, and drawn in
%high noise level. The reconstitution problem is then to estimate the molecule
%from this data.

>>>>

%
%In this section, we provide the details of the 2D experiment shown in Figure~\ref{fig:example}. In the experiment, we generated a sequence of $767\times 10^3$ 2D images (``micrograph") of size $2000\times 2000$. Each micrograph had around $\sim 900$ signal occurrences (depends on the stopping criterion that we need to explain) and in total $M = 561\times 10^6$. The noise level was $\sigma=1$.  
%
%To accelerate the experiment, we estimated only the first two autocorrelations of the signal. As mentioned in Section~\ref{sec:estimating_ac}, this data determines a 2D signal uniquely, up to possible reflection symmetry. 
%In this experiment, we chose the correct reflection manually. To estimate the signal we used the Relax-Reflect-Reflect (RRR) algorithm, which is a known phase retrieval algorithm. Recall that the second-order autocorrelation is equivalent to the power spectrum of the signal.
%Starting form random initialization of size $(2L-1)\times(2L-1)$, its $k$th  iteration take the form of 
% \begin{equation*}
% x_k = x_{k-1} + \beta(P_2(2P_1(x_{k-1}) -x_{k-1}) - P_1(x_{k-1}), 
%  \end{equation*}
% where $P_1$ is a projection that keeps the values of the  $L\times L$ entries in the upper-left corner and zeros out all other entries, $P_2$ is a projection that keeps the Fourier phase of $x_{k-1}$ and impose the correct Fourier magnitudes, and we set $\beta = 0.5$. The solution of the RRR scheme was used to initialized a LS estimation on the first two moments with signals of length $(2L-1)\times(2L-1)$ for the 200 iterations. Finally, we chose the $L\times L$ upper left corner and refined it using LS with 500 iterations. 
%

\section{Open questions}

In this paper, we considered the problem of estimating a set of signals from their multiple occurrences in unknown locations in the data.  We focused on  low $\SNR$ environments in which detection is impossible. 
Our technique  is based on computing the third-order autocorrelation function of the data with asymptotic estimation rate proportional to $\sigma^6/M$. Based on related results in multireference alignment~\cite{abbe2018estimation}, we believe that it is the optimal estimation rate, however, this is yet to be proven.

Our results rely on two main assumptions that are not necessarily met by applications. 
First, we modeled the background information as i.i.d.\ additive noise. In practice,
the background information may be structured, and even signal-dependent. Then, the question is  under what conditions  
one can still estimate the signals and separate them from the background information in the low $\SNR$ regime?

In addition, we assumed that the signal occurrences are all separated by $L-1$ entries, see~\eqref{eq:spacing}. If the signals are not separated, one can introduce a new variable $p$ that represents the distribution of the spacing between signal occurrences. The first entry $p[1]$ will represent the probability that two consecutive signals are separated by only one entry, $p[2]$ the probability for spacing of two entries and so on. Using this new variable $p$, one can write explicitly the relation between the autocorrelation functions of the data and those of the signal in a similar way to~\eqref{eq:data_ac}. Under what conditions on $p$ and the signals one can still estimate the signals from the data?

\section{Connection with the cryo--EM problem}

Cryo--EM is an innovative technology for reconstructing the 3D structure of macromolecules. In recent years, structures
of many molecules, previously regarded as insurmountable, are now being
obtained to near-atomic resolution; see for instance~\cite{kuhlbrandt2014resolution,bartesaghi20152}. This technological advancement was recognized by the 2017 Nobel Prize in Chemistry~\cite{nobel}.

In a cryo--EM experiment, the biological samples of the (ideally) same molecule are rapidly frozen in a thin layer of vitreous ice. Within the ice, the molecules are randomly oriented and positioned. Then,  the microscope produces a 2D tomographic projection image, called a \emph{micrograph}, of the multiple samples embedded in the ice. Importantly, the micrograph is dominated by noise due to the small electron doses that
can be applied to the specimen without causing radiation damage.

The cryo--EM problem is to estimate the structure of the molecule from the micrograph (or several micrographs). 
 All current methods in the field split the reconstruction procedure to several subroutines. The first step in all methods is the so called particle picking, detecting the 2D tomographic projections of the samples from the noisy micrograph. The output of ideal particle picker is a series of 2D images, each contains one centered tomographic projection associated with unknown 3D orientation. These series of images 
 is then used by a variety of algorithms to reconstruct the structure. 
However, due to the high noise level, the performance of the particle pickers  is not ideal. For instance, the projections in the 2D images are typically not centered, increasing dramatically the number of parameters involved in the estimation problem. In addition, the information of particles that are too close to each other is usually neglected. Hence, valuable information that can be used is omitted.

The model considered in this paper can be interpreted as a preliminary step towards investigation of the possibility to \emph{estimate the molecule's structure directly from the micrograph}. 
In our model, the noisy data is the analog of the micrograph. The $K$ sought signals correspond to $K$ different molecule's projections, taken from different orientations in $SO(3)$. In tomography, if enough projections are estimated, then one can estimate the whole structure (up to some $K$-dependent resolution).
The position of individual projections are the nuisuance varialbles in the cryo--EM problem, in analogy to the individual signal's locations in our setup.

Clearly, applying the autocorrelation method to the cryo--EM problem raises interesting challenges that are far beyond the scope of this paper. 
For instance, the numerical experiments of Section~\ref{sec:numerics} indicate that we need a huge number of observations to get accurate estimate. Can we accelerate the estimation rate so we can apply this method with smaller amount of data? In addition, since the size of a micrograph is quite large (typically around $4000\times 4000$ pixels), computing the third-order autocorrelations may be  expensive if not implemented carefully by parallelizing the computations.
Also, the model should incorporate minimal spacing between the samples on the micrograph.
